### 2013-08-13 Tex/chapters/results.tex
abstand hinter fig. und tab. korrigiert

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N} H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{sssec:eqtime}). The used values for different system sizes
are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\). Not only the seed to generate the new random
realization of the proximity graph gets changed, but also the seed for
the random numbers used in the Monte Carlo simulation and during the
generation of the random start configuration of the spins.\\
The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
over different realizations of the random proximity graph, which are
surely uncorrelated.
Because every error mentioned in this thesis is of this type, it is not
necessary to determine \(\tau\) for each observable. Therefore a good
error estimate can be achieved by simple bootstrapping. Though one has
to simulate enough uncorrelated states for each realization, to keep
the \(\Delta \overline{\avg{O}}\) small. For every determined value an
error is calculated and given in the form \texttt{value(error of last digit)}.
The error given for fits are the asymptotic standard errors as calculated
by gnuplot\footnote{An open source plotting program, used for all plots and fits in this thesis. \url{http://gnuplot.info/}.}.

\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
\label{ssec:results:autocorr}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) is given, to illustrate the benefits
    of the used Wolff cluster algorithm.\\
    In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at
    \(\sigma=0\) is plotted. Note, that these are the unrounded values
    of tab. \ref{tab:tauAndTeq}
    \begin{figure}[htbp]
        \centering
        \subfigure[in Dependence on the Temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in Dependence on the System Size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The Autocorrelation Time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
                are the standard error determined by bootstrapping)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff algorithm. At low temperatures it flips nearly every
    spin in every step, thus the correlation drops to zero after one sweep.
    Alternatively the parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law \(\tau \propto L^z\), which is
    the expected behavior of a dynamical exponent \(z\) as mentioned in
    section \ref{sssec:eqtime}.
    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
    not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
    for the Wolff cluster algorithm. On the one hand the number of sweeps
    in which \(\tau\) is measured in this thesis are more than a standard
    Metropolis sweep to which \(z\) normally corresponds, because each sweep
    alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
    flipped. On the other hand the \(\tau\) used for the fit are not the
    \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
    Nevertheless it is interesting, that it obeys a power law
    \(\tau \propto L^{z'}\) just the same. This suggests, that \(\xi \gtrsim L\)
    is satisfied at the temperature of maximum \(\tau\), which is plausible,
    because the peak in fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
    is near \(T_{c}\).\\
    Anyhow, fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
    This is of course only a rough analysis of existing data which was
    generated for another purpose. For a more in depth inspection, one
    would perform the simulation at the critical point, which will be
    determined in the next sections.

\subsection{Finite Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\) (here with a RNG).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$.\\
            \subref{sfig:smeared_out:meanM}: Effects of different system
            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
        }
        \label{fig:smeared_out}
    \end{figure}\\
    But in the shown plots there occurs no steep decline to zero, but a
    smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finte size effects}.
    These finite size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as is visible
    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999}, which also yield the critical
    exponents. This will be performed in the next section.
    Though there is an easier approach, which yields comparable precise
    values for \(T_{c}\) in a much faster and more robust way, which is
    presented in \ref{ssec:binderIntersections}.

@@

    Like the obersables from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.

@@

                size scaling (errors are for clarity not given, see tab. \ref{tab:critExp})

@@

    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}

@@

    in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}

@@

                size scaling (for error estimates see tab. \ref{tab:critExp})\\

@@

                size scaling (for error estimates see tab. \ref{tab:critExp})

@@

    chapter in fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
    The determined values are displayed in tab. \ref{tab:critExp}.

@@

    Like in tab. \ref{tab:critExp} to see, most values

@@

    many measurements in the vicinity of \(T_c\) (compare fig. \ref{sfig:gettingCrit:s_1_sus}),

@@

    The results are displayed in fig. \ref{fig:susCrossCheck}. The ratios

@@

    As an example take fig. \ref{fig:gettingCrit:binder_fit_s_0}.

@@

    And in tab. \ref{tab:critTemp} the values are displayed together with the

@@

    These values of \(T_c\) are plotted over \(\sigma\) in fig. \ref{fig:Tc}.

@@

    in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},

@@

    In fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}

@@

    graph. This is done in fig. \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.

@@

        \caption[Critical Temperature Normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    To understand the jump of \(T_c\), it seems to be sufficient to
    understand the jump of \(K\), which is easily explained
    by the definition of the GG and its aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.\\
    Further the increase of \(T_c\) on the GG can be made plausible.
    Though it is not removed by the normalization, it is reduced. Also
    the maximum of the \(K\) is at the same \(\sigma\), as the maximum
    of \(T_c\). So while displacing the nodes, there arise more edges
    than edges are vanishing until \(\sigma \approx 0.15\) is reached.
    Then more edges disappear, than appear at further displacement. This
    is not an obvious effect, but can be seen in fig. \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
    \begin{figure}[htbp]
        \subfigure[][$\sigma = 0.00$]
        {
            \label{sfig:GG_sigma:0.00}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][$\sigma = 0.01$]
        {
            \label{sfig:GG_sigma:0.01}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
        }

@@

        \caption[Examples of RNG for different $\sigma$]
        {
            RNG with periodic boundary conditions for different \(\sigma = 0\)
        }
        \label{fig:RNG_sigma}
    \end{figure}\\
    But the degree does not alone influence the behavior of \(T_c\).
    Further \(T_c\) depends on the coupling constant \(J\), which is
    obvious in eq. \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
    coupling constant in turn is depending on the length of the edges,
    which changes with \(\sigma\).
    Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted. This is a number which should combine the dependence on
    the degree and the coupling constant. It is determined by summing
    over the edge weights of all edges connected to a node and averaging
    this value over all nodes. Alternatively it is the average edge weight
    of all edges multiplied by the degree.
    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

@@

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g_c\) is
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses another definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match its definition in this thesis.}.
    Because the analysis of section \ref{ssec:binderIntersections}
    yields \(g_c\) anyway, it is easy to check the consistency and
    behavior of \(g_c\) in the disordered Ising model.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder Cumulant at the Critical Point $g_c$]
        {
            Values of the Binder cumulant at the critical point \(g_c\)
            for\\
            \subref{sfig:TcG:RNG} a RNG and\\
            \subref{sfig:TcG:GG} a GG for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in fig. \ref{fig:TcG}, \(g_c\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviations are only very small. Perhaps this overestimation is caused
    by the cubic spline interpolation used to acquire these \(g_c\) values.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
    lattice structure has a minor effect on \(g_c\), the uncertainty of
    \(g_c\) is too big, to show it. For a more in depth analysis, new
    Monte Carlo simulations at \(T_c\) would be needed. But this is
    beyond the scope of this thesis. Anyway the results are the expected
    behaivior, because no major deviations from the value of \(g_c\) at
    \(\sigma = 0\) occur at larger \(\sigma\).

>>>>

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N} H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{sssec:eqtime}). The used values for different system sizes
are listed in tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\). Not only the seed to generate the new random
realization of the proximity graph gets changed, but also the seed for
the random numbers used in the Monte Carlo simulation and during the
generation of the random start configuration of the spins.\\
The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
over different realizations of the random proximity graph, which are
surely uncorrelated.
Because every error mentioned in this thesis is of this type, it is not
necessary to determine \(\tau\) for each observable. Therefore a good
error estimate can be achieved by simple bootstrapping. Though one has
to simulate enough uncorrelated states for each realization, to keep
the \(\Delta \overline{\avg{O}}\) small. For every determined value an
error is calculated and given in the form \texttt{value(error of last digit)}.
The error given for fits are the asymptotic standard errors as calculated
by gnuplot\footnote{An open source plotting program, used for all plots and fits in this thesis. \url{http://gnuplot.info/}.}.

\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
\label{ssec:results:autocorr}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) is given, to illustrate the benefits
    of the used Wolff cluster algorithm.\\
    In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at
    \(\sigma=0\) is plotted. Note, that these are the unrounded values
    of tab.\ \ref{tab:tauAndTeq}
    \begin{figure}[htbp]
        \centering
        \subfigure[in Dependence on the Temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in Dependence on the System Size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The Autocorrelation Time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
                are the standard error determined by bootstrapping)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff algorithm. At low temperatures it flips nearly every
    spin in every step, thus the correlation drops to zero after one sweep.
    Alternatively the parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law \(\tau \propto L^z\), which is
    the expected behavior of a dynamical exponent \(z\) as mentioned in
    section \ref{sssec:eqtime}.
    In fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
    not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
    for the Wolff cluster algorithm. On the one hand the number of sweeps
    in which \(\tau\) is measured in this thesis are more than a standard
    Metropolis sweep to which \(z\) normally corresponds, because each sweep
    alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
    flipped. On the other hand the \(\tau\) used for the fit are not the
    \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
    Nevertheless it is interesting, that it obeys a power law
    \(\tau \propto L^{z'}\) just the same. This suggests, that \(\xi \gtrsim L\)
    is satisfied at the temperature of maximum \(\tau\), which is plausible,
    because the peak in fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
    is near \(T_{c}\).\\
    Anyhow, fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
    This is of course only a rough analysis of existing data which was
    generated for another purpose. For a more in depth inspection, one
    would perform the simulation at the critical point, which will be
    determined in the next sections.

\subsection{Finite Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. In fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\) (here with a RNG).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$.\\
            \subref{sfig:smeared_out:meanM}: Effects of different system
            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
        }
        \label{fig:smeared_out}
    \end{figure}\\
    But in the shown plots there occurs no steep decline to zero, but a
    smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finte size effects}.
    These finite size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as is visible
    in fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999}, which also yield the critical
    exponents. This will be performed in the next section.
    Though there is an easier approach, which yields comparable precise
    values for \(T_{c}\) in a much faster and more robust way, which is
    presented in \ref{ssec:binderIntersections}.

@@

    Like the obersables from fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:binder_s_0}
    collapse in fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.

@@

                size scaling (errors are for clarity not given, see tab.\ \ref{tab:critExp})

@@

    Analogical fig.\ \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}

@@

    in fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}

@@

                size scaling (for error estimates see tab.\ \ref{tab:critExp})\\

@@

                size scaling (for error estimates see tab.\ \ref{tab:critExp})

@@

    chapter in fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.)
    The determined values are displayed in tab.\ \ref{tab:critExp}.

@@

    Like in tab.\ \ref{tab:critExp} to see, most values

@@

    many measurements in the vicinity of \(T_c\) (compare fig.\ \ref{sfig:gettingCrit:s_1_sus}),

@@

    The results are displayed in fig.\ \ref{fig:susCrossCheck}. The ratios

@@

    As an example take fig.\ \ref{fig:gettingCrit:binder_fit_s_0}.

@@

    And in tab.\ \ref{tab:critTemp} the values are displayed together with the

@@

    These values of \(T_c\) are plotted over \(\sigma\) in fig.\ \ref{fig:Tc}.

@@

    in fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},

@@

    In fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}

@@

    graph. This is done in fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.

@@

        \caption[Critical Temperature Normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    To understand the jump of \(T_c\), it seems to be sufficient to
    understand the jump of \(K\), which is easily explained
    by the definition of the GG and its aftereffects for
    the transition from \(\sigma = 0\). Visible in fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.\\
    Further the increase of \(T_c\) on the GG can be made plausible.
    Though it is not removed by the normalization, it is reduced. Also
    the maximum of the \(K\) is at the same \(\sigma\), as the maximum
    of \(T_c\). So while displacing the nodes, there arise more edges
    than edges are vanishing until \(\sigma \approx 0.15\) is reached.
    Then more edges disappear, than appear at further displacement. This
    is not an obvious effect, but can be seen in fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
    \begin{figure}[htbp]
        \subfigure[][$\sigma = 0.00$]
        {
            \label{sfig:GG_sigma:0.00}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][$\sigma = 0.01$]
        {
            \label{sfig:GG_sigma:0.01}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
        }

@@

        \caption[Examples of RNG for different $\sigma$]
        {
            RNG with periodic boundary conditions for different \(\sigma = 0\)
        }
        \label{fig:RNG_sigma}
    \end{figure}\\
    But the degree does not alone influence the behavior of \(T_c\).
    Further \(T_c\) depends on the coupling constant \(J\), which is
    obvious in eq. \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
    coupling constant in turn is depending on the length of the edges,
    which changes with \(\sigma\).
    Therefore  in fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted. This is a number which should combine the dependence on
    the degree and the coupling constant. It is determined by summing
    over the edge weights of all edges connected to a node and averaging
    this value over all nodes. Alternatively it is the average edge weight
    of all edges multiplied by the degree.
    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

@@

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g_c\) is
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses another definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match its definition in this thesis.}.
    Because the analysis of section \ref{ssec:binderIntersections}
    yields \(g_c\) anyway, it is easy to check the consistency and
    behavior of \(g_c\) in the disordered Ising model.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder Cumulant at the Critical Point $g_c$]
        {
            Values of the Binder cumulant at the critical point \(g_c\)
            for\\
            \subref{sfig:TcG:RNG} a RNG and\\
            \subref{sfig:TcG:GG} a GG for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in fig.\ \ref{fig:TcG}, \(g_c\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviations are only very small. Perhaps this overestimation is caused
    by the cubic spline interpolation used to acquire these \(g_c\) values.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
    lattice structure has a minor effect on \(g_c\), the uncertainty of
    \(g_c\) is too big, to show it. For a more in depth analysis, new
    Monte Carlo simulations at \(T_c\) would be needed. But this is
    beyond the scope of this thesis. Anyway the results are the expected
    behaivior, because no major deviations from the value of \(g_c\) at
    \(\sigma = 0\) occur at larger \(\sigma\).
